\section{Triggers}
    Much like an oscilloscope that has a trigger mechanism to capture periodic signals or investigate a transient event \cite{osc-t}, the $\Delta$Q oscilloscope has a similar mechanism that can recognise when an observed $\Delta$Q violates certain conditions regarding required behaviour and record snapshots of the system.

    Each time an observed $\Delta$Q of a sampling window is calculated, it is checked against the requirements set by the user. If these requirements are not met, a trigger is fired and a snapshot of the system is saved to be shown to the user. 
    
    \subsection{Snapshot}
    A snapshot of the system gives insights into the system before and after a trigger was fired. It gives the user a \textit{still} of the system, as if it was frozen in time.
    
    We can define a \textbf{``snapshot window''} which is equal to the polling window when no triggers are fired. The maximum size of the snapshot window under normal conditions (no triggers fired) is 30 $\Delta$Qs, like the polling window.  All the $\Delta$Qs which are observed and calculated in a polling window are stored away in both the snapshot and polling windows. Then, if no trigger is fired, older $\Delta$Qs are removed from both.

    Instead, if a trigger is fired, the $\Delta$Qs sampled for the next 5 seconds are added to the snapshot window, without removing older ones from the window. This it to allow the user to look at the state of the system before and after the trigger. After these 5 seconds the recorded snapshot window will contain the 30 $\Delta$Qs before the trigger being fired, which is equal to the polling window before the trigger, plus the $\Delta$Qs sampled in the 5 seconds after the trigger being fired. This snapshot window is stored away and can be observed by the user.

The polling window will always keep 30 $\Delta$Qs, it still follows the same strategy of removing older $\Delta$Qs, even if a trigger was fired. Meanwhile, the snapshot window's maximum size increases during the recording of one, keeping older $\Delta$Qs even if the size of the snapshot window is $>$ 30. When the snapshot finishes recording at a time $t$, the snapshot window will be the same as the polling window at time $t$, they will contain the same $\Delta$Qs. 
