\chapter*{Acknowledgments}
    This thesis is the culmination of my studies, I would like to thank the people who made this possible, those who supported me through the years and those who helped my with the thesis.
    
    \forceindent My family, especially \textbf{my mom, my dad, my brother} and \textbf{my sister}, for their help which was a crucial shoulder I could lay on while writing this thesis and most importantly throughout these five years.
    
    \forceindent My \textbf{friends}, to those who have taken time out of their lives to listen the thesis presentation and to those who through the years have been there for me. 

    \forceindent \textbf{A-M.}, for the moments we shared these four years together in uni.

    \forceindent \textbf{My dad} and \textbf{Maurizio}, who nurtured the passion for coding in me.
    
    \forceindent \textbf{Peer Stritzinger}, \textbf{Stritzinger GmbH} and the \textbf{EEF Observability Working Group} (Bryan Naegele and Tristan Sloughter) for their help in the EEF Slack, which helped me in understanding OpenTelemetry and gave me the send\_after intuition.

    \forceindent \textbf{Neil Davies} for taking the time to proofread my thesis.

    \forceindent The \textbf{PNSol Ltd.} team for their extensive groundwork on \textbf{$\Delta$QSD} and its dissemination, which made this thesis possible.

    \forceindent Lastly, \textbf{Peter Van Roy}, for his year-long relentless interest, support and weekly and constant supervision which made sure the project would come to fruition. 

