\section{Dashboard}
    The dashboard is devised of multiple sections where the user can interact with the oscilloscope, create the system, observe the behaviour of its components, set triggers.

    \subsection{Sidebar}
        The sidebar has multiple tabs, we explain here the responsibility of each one.

    \subsubsection{System/Handle plots tab}

    \paragraph{System creation}
        In this tab the user can create its system using the grammar defined before, he can save the text he used to define the system or load it, the system is saved to a file with any extension, we nevertheless define an extension to save the system to, the extension \texttt{.dq}.
        If the definition of the input is wrong, he will be warned with a pop up giving the error the parser generator encountered in the creation of a system.

    \paragraph{Adding a plot}
        Once the system is defined, the user can choose the probes he wants to plot. They can select multiple probes per plot and display multiple plots on the oscilloscope window.
    
    \paragraph{Polling rate}
        The user can choose the polling rate of the system: How often $\Delta$Qs are calculated and displayed in the oscilloscope.

    \paragraph{Editing a plot}
        By clicking onto a plot that is being shown, the user can choose to add or remove probes to and from it. Multiple probes can be selected to either be removed or added.

    \subsubsection{Parameters tab}
        In this tab, the user can define parameters for the probes they have defined.

    \paragraph{Set a QTA}
        The user is given the choice to set a QTA for a given observable, they have 4 fields where they can fill in which correspond to the percentiles and the maximum amount of failures allowed, they can change this dynamically during execution.

    \paragraph{dMax, bins}
        The user has a slider which goes from -10 to 10, where they can set the parameters we explained previously, $n$, the exponent of $\Delta_{tbase} \cdot 2^n$ and the bins $N$. When these informations are saved by the user, the new $dMax$ is transmitted to the stub and saved for the selected observable.

    \subsubsection{Triggers tab}
        In the triggers tab the user can set triggers and observe the snapshots of the system.

    \paragraph{Set triggers}
        The user can set which triggers to fire for the probes they desire, they are given checkboxes to decide which ones to set as active or not (by default, the triggers are deactivated).
    
    \paragraph{Fired triggers}
        Once a trigger is fired, the system start a timer, during which all probes start recording the observed $\Delta$Qs (and the calculated ones if applicable) without discarding older ones. Once the timer expires, the snapshot is saved for the user in the triggers tab. In the dashboard, it indicates when the trigger was fired (timestamp) and the name of the probe which fired it.
    
    \subsection{Plots window}
        To the left, the main window shows the plots of the probes being updated in real time. 

    \subsection{Stub controls}
        Below the sidebar, two buttons are present, these buttons communicate to the stub. 
         
        The \textbf{start stub} button sends a message to the stub, telling it to start sending spans. The \textbf{stop stub} button stops it.
