\section{Context}
    $\Delta$QSD is an industrial-strength approach for large-scale system design that can predict performance and feasibility early on in the design process.  
    Developed over 30 years by a small group of people around Predictable Network Solutions Ltd, the paradigm has been applied in various industrial-scale problems with huge success and large savings in costs. \cite{dq-tut}
     This project will develop a practical tool, the \textbf{$\Delta$Q Oscilloscope}, for the Erlang developer community. 
    
    The Erlang language and Erlang/OTP platform are widely used to develop distributed applications that must perform reliably under high load. The tool will provide useful information for these applications both for understanding their behaviour, for diagnosing performance issues, and for optimizing performance over their lifetime. 
    
    The $\Delta$Q Oscilloscope will perform statistical computations to show real time graphs about the performance of system components. With the oscilloscope prototype we will present in this paper, we are aiming to show that the $\Delta$QSD paradigm is not only a theoretical paradigm, but it can be employed in a tool to diagnose large distribute systems.  

    Modern software development practices successfully fail to adequately consider essential quality requirements or even to consider properly whether a system can actually meet its intended outcomes, particularly when deployed at scale, the $\Delta$QSD paradigm addresses this problem! 
    
    The oscilloscope targets large distributed applications handling many independent tasks where performance and reliability are important. 
    
    $\Delta$QSD has important properties which make its application to distributed projects interesting, it supports:
    \begin{itemize}
        \item A compositional approach that considers performance and failure as first-class citizens. 
        \item Stochastic approach to capture uncertainty throughout the design approach.
        \item Performance and feasibility can be predicted at high system load for partially defined systems
    \end{itemize}
    
    While the paradigm has been successfully applied in \textbf{a posteriori} analysis, there is no way yet to analyse a distributed system which is running in real time! This is where the $\Delta$Q oscilloscope comes in. 
